---
title: "Untitled"
author: "satsuki gyoten"
date: "2023-10-11"
output: html_document
---

1
a)objective
b)subjective
c)objective
d)subjective
e)objective

2
a)empirical
b)classical
c)empirical

3
a)simple
b)simple
c)compound
d)simple
e)compound

4
a)independent
b)mutually exclusive and collectively exhaustive
c)independent
d)mutually exclusive
e)mutually exclusive and collectively exhaustive

5
a)true
b)false
c)true

6
it will be 1

7
```{r}
Pr_d<- 1-(0.23+0.15+0.46)
Pr_d+0.23
```
 0.39
 


8
it is 0

9
```{r}
0.13*0.36
```
0.0468

10
0.5=0.3+x-0.3x
x=2/7
answer: 2/7

11
0.7=0.4+x-0.4x
x=1/2
answer: 1/2

12
0.6=0.4+x-0.4x
x=1/3
answer: 1/3

13
```{r}

12*11*10*9*8

1/6



```
a) 12*11*10*9*8= 95040
b) 1/6
c) 12!/5!*7!= 792
d)7!/ 2!*5!=21
e)12*11=132
f)7*6=42

14
6C2* 5C2* 4C1=600

15
6!= 720

16
a) 15C6= 5005
b) 10C3 *5C3= 120*10= 1200
c) 10C4* 5C2 = 210* 10= 2100

17
(1/52)^1*(3/52)^3*4C1
=36/52^4

18
(3/52)^3*(1/52)^2* 5C2
=90/ 52^5

19
7: 3/18= 1/6
3:1/18

20
0.8*0.5/0.8:0.5+0.3*0.5+0.1*0.5
=0.4/0.6
=2/3

21
not found

22
It is better to change the doors because the possibility of opening a door with cars will increase if you change.
Assume you have opened the door of nubmer 1 in 1-3 doors.
A1:the treasure is at door 1
A2:the treasure is at door 2
A3:the treasure is at door 3
B1:the man opens door 2
B2:the man opens door 3

when you don't change
P(A1|B3) Probability of finding treasure in door 1 when man opens door 3
=1/3
P(A1|B2) Probability of finding treasure in door 1 when man opens door 
2=1/3

when you change
P(A3|B2)Probability of finding treasure in door 3 when man opens door2 
=2/3
P(A2|B3)Probability of finding treasure in door 2 when man opens door3
=2/3

As you can see, the probability doubles when you chage it.


23
a) 0.3*0.5+ 0.3*0.4 +0.4*0.3 = 0.39 →39%
b) P(C|V) =P(C) * P(V|C) / P(V) = 0.3*0.5/ 0.39 →38%
c) P(L|V) =P(L) * P(V|L) / P(V)=0.3*0.4/ 0.39 →30%
d) P(I|V) =P(I) * P(V|I) / P(V)=0.4*0.3/ 0.39 →30%

24
0.62/ 0.38 =1.63 or 31:19

25
x1=3/1 X2=1/2
(3/1)/(1/2)=6 →6

26
Unemployed people are 1.42(142%)more likely than employed people, 
and peolple who has a college degree are 0.62(62%)less likely.
