---
title: "B1 HW"
author: "satsuki gyoten"
date: "2023-09-20"
output: html_document
---

```{r}
library(readr)
songs1 <- read_csv("B1/songs1.csv")

library(readr)
songs2 <- read_csv("B1/songs2.csv")

library(readr)
users1 <- read_csv("B1/users1.csv")

library(readr)
users2 <- read_csv("B1/users2.csv")
```


```{r}

library(tidyverse)
##Q1
##experiment1

result<- users1 %>%
group_by(world_id)%>%
summarise(n = n())

prop<- prop.table(result$n)
table_prop1<-tibble(World_id=c("social","indep"),
prop=prop
)
View(table_prop1)

##experiment2
result2<- users2 %>%
group_by(world_id)%>%
summarise(n = n())

prop2<- prop.table(result2$n)
table_prop2<-tibble(World_id=c("social","indep"),
prop=prop2
)

View(table_prop2)
```


```{r}
##Q2
users1_indep<- users1[ users1 $world_id=="9",] ## 1:a set of independent condition
users1_social<- users1[ users1 $world_id=="1",] ##1:a set of social influence 

users2_indep<- users2[ users2 $world_id=="9",] ## 2:a set of independent condition
users2_social<- users2[ users2 $world_id=="1",] ## 2:a set of social influence 


##experiment1
round(mean(users1_indep$download),3)## control condition
round(mean(users1_social$download),3)## treatment condition



##experiment2
round(mean(users2_indep$download),3)## control condition
round(mean(users2_social$download),3)## treatment condition




##experiment1 number of times listened
songs1_indep<- songs1$listen_indep ## 1:a set of independent condition
songs1_social<-songs1$listen_soc ##1:a set of social influence

round(mean(songs1_indep),3)## control condition
round(mean(songs1_social),3)## treatment condition


##experiment2 number of times listened
songs2_indep<- songs2$listen_indep ## 2:a set of independent condition
songs2_social<- songs2$listen_soc ## 2:a set of social influence

round(mean(songs2_indep),3)## control condition
round(mean(songs2_social),3)## treatment condition


```
answers

experiment1
control (independent) 47.155
treatment (social influence) 42.242
There is no significant difference between the treatment and control variables.


experiment2
control (independent) 124.127
treatment (social influence) 301.237
Treatment variables had about 2.5 times more downloads than control variables.

mean of the number listened
experiment1
control (independent) 112.375
treatment (social influence) 51.271
experiment2
control (independent) 117.562
treatment (social influence) 51.146


```{r}
#Q3
#experiment1 download

songs1_indep_download<- songs1$down_indep ## 1:a set of independent condition
songs1_social_download<- songs1$down_soc## 1:a set of social influence

library(ineq)
round(ineq(songs1_indep_download),3)
round(ineq(songs1_social_download),3)

#experiment2 download
songs2_indep_download<- songs2$down_indep ## 2:a set of independent condition
songs2_social_download<- songs2$down_soc## 2:a set of social influence

round(ineq(songs2_indep_download),3)
round(ineq(songs2_social_download),3)

#experiment1 listen
round(ineq(songs1_indep),3)
round(ineq(songs1_social),3)

#experiment2 listen
round(ineq(songs2_indep),3)
round(ineq(songs2_social),3)

```
For both the download and listening variables,in Experiment 1 there was no significant difference in the Gini coefficient between the treatment (social impact) and control (independent) groups, but in Experiment 2, the treatment (social impact) group was significantly more unequal than the control (independent) group.


```{r}
#Q4
#experiment1 
round(mean(users1_indep$web),3)
round(mean(users1_social$web),3)


round(mean(users1_indep$visit),3)
round(mean(users1_social$visit),3)


round(mean(users1_indep$purchase),3)
round(mean(users1_social$purchase),3) 

#experiment2
round(mean(users2_indep$web),3)
round(mean(users1_social$web),3)

round(mean(users2_indep$visit),3)
round(mean(users2_social$visit),3)


round(mean(users2_indep$purchase),3)
round(mean(users2_social$purchase),3)

```
For all web/ visit/ purchase variables, there were no significant differences between the treatment (social influence) and control (independent) groups in both Experiment 1 and Experiment 2.

This indicates that the inequality of downloads and listens shown in the previous question were not influenced by other variables.

```{r}

```

```{r}

```