---
title: "B1 HW"
author: "satsuki gyoten"
date: "2023-09-20"
output: html_document
---

```{r}
library(readr)
songs1 <- read_csv("B1/songs1.csv")

library(readr)
songs2 <- read_csv("B1/songs2.csv")

library(readr)
users1 <- read_csv("B1/users1.csv")

library(readr)
users2 <- read_csv("B1/users2.csv")
```


```{r}

library(tidyverse)
##Q1
##experiment1

result<- users1 %>%
group_by(world_id)%>%
summarise(n = n())

prop<- prop.table(result$n)
table_prop1<-tibble(World_id=c("social","indep"),
prop=prop
)
View(table_prop1)

##experiment2
result2<- users2 %>%
group_by(world_id)%>%
summarise(n = n())

prop2<- prop.table(result2$n)
table_prop2<-tibble(World_id=c("social","indep"),
prop=prop2
)

View(table_prop2)
```


```{r}
users1_indep<- users1[ users1 $world_id=="9",] ## 1:a set of independent condition
users1_social<- users1[ users1 $world_id=="1",] ##1:a set of social influence 

users2_indep<- users2[ users2 $world_id=="9",] ## 2:a set of independent condition
users2_social<- users2[ users2 $world_id=="1",] ## 2:a set of social influence 


##experiment1
round(mean(users1_indep$download),3)## control condition
round(mean(users1_social$download),3)## treatment condition



##experiment2
round(mean(users2_indep$download),3)## control condition
round(mean(users2_social$download),3)## treatment condition




##experiment1 number of times listened
songs1_indep<- songs1$listen_indep ## 1:a set of independent condition
songs1_social<-songs1$listen_soc ##1:a set of social influence

round(mean(songs1_indep),3)## control condition
round(mean(songs1_social),3)## treatment condition


##experiment2 number of times listened
songs2_indep<- songs2$listen_indep ## 2:a set of independent condition
songs2_social<- songs2$listen_soc ## 2:a set of social influence

round(mean(songs2_indep),3)## control condition
round(mean(songs2_social),3)## treatment condition


```
answers

experiment1
control (independent) 47.155
treatment (social influence) 42.242
There is no significant difference between the treatment and control variables.


experiment2
control (independent) 124.127
treatment (social influence) 301.237
Treatment variables had about 2.5 times more downloads than control variables.

mean of the number listened
experiment1
control (independent) 112.375
treatment (social influence) 51.271
experiment2
control (independent) 117.562
treatment (social influence) 51.146


```{r}

```

```{r}

```

```{r}

```

```{r}

```