---
title: "B2 HW (indiscriminate-violence)"
author: "satsuki gyoten"
date: "2023-09-20"
output: html_document
---

```{r}
library(readr)
chechen <- read_csv("B1/chechen.csv")

library(dplyr)
library(tidyverse)

chechen_fire<- chechen[chechen$fire == 1,]
chechen_nonfire<- chechen[chechen$fire == 0,]

```


```{r}
##Q1
q1<-table(chechen$fire)
q1
prop.table(q1)


```

Towns that were attacked and those that were not attacked are 159 each, with a percentage of 50% each.


```{r}
##Q2

chechen_groznyy<- chechen[chechen$groznyy==1,]
chechen_village<- chechen[chechen$groznyy==0,]

summary(na.omit(chechen_groznyy))
summary(na.omit(chechen_village))

```
In terms of mean, the death in Groznyy was 3.714, while that of the villages outside was 1.572. In terms of median,the death in Groznyy was 3.000 , while that of the villages outside was 0.00.


```{r}
##Q3

summary(chechen_fire$postattack)
summary(chechen_nonfire$postattack)

```
The average number of insurgent attacks with artillery fire was 1.497, while the average number of attacks in a village without artillery fire was 2.05. For the quartiles, the number of insurgent attacks with artillery fire was respectively  0.000 (25%),0.000 (50%), 1.000 (75%)while the number of attacks in the villages without artillery fire was 0.000 (25%),0.000 (50%), 2.00 (75%)


```{r}


```

```{r}


```

```{r}


```