---
title: "A3"
author: "satsuki gyoten"
date: "2023-09-27"
output: html_document
---

```{r}
library(readr)
ANES <- read_csv("A3/ANES.csv")
library(dplyr)
library(ggplot2)

```

```{r}
# part2-1
ANES$VEP_turnout<- ANES$votes/ANES$VEP *100

# 2
head(ANES$VEP_turnout)
```

The first value was as expected. The unit of measurement is percent.

```{r}
# 3
ANES$VAP_turnout<- ANES$votes/ANES$VAP *100


# 4
head(ANES$VAP_turnout)

```

The first value was as expected. The unit of measurement is percent.

```{r}
# 5
```

VEP turnout is always higher.
This is because VAP includes not only VEP but also felons and non-citizens, which do not have the right to vote.
Here, the denominator is VAP>VEP, therefore the actual value is VAP<VEP.

```{r}
# 6
mean(VEP_turnout)

```
This number shows the national average of voter turnout calculated for VEP. Units are in percentages.

```{r}
# 7
mean(ANES$ANES_turnout)

```
This number shows the national average of voter turnout calculated for ANES respondents who reported to have voted in election. Units are in percentages.

```{r}
# 8
```
Clearly, ANES_turnout is higher than VEP_turnout. This indicates a social desirability bias in the observations in ANES.

```{r}
# part 3-1

ANES$turnout_bias<- ANES$ANES_turnout - ANES$VEP_turnout

# 2
head(ANES$turnout_bias)

```
The first value was as expected. The unit of measurement is percent.

```{r}
# 3
plot(ANES$year,ANES$turnout_bias)

```
All values are positive, and the variable looks normally distributed.

```{r}

```

