---
title: "B3 HW"
author: "satsuki gyoten"
date: "2023-10-14"
output: html_document
---
chapter1 problem22



Let the six children be three boys, each with ABC, and three girls, each with 123.
Consider the order in which they are born as frames.
First, for the first three frames (first born), the permutation of 123 is,
3*2*1=6.
Then, for the second three frames, the  three frames  (born later) is
3*2*1=6.
Hence, the number if the top three are girls is 6*6.


On the other hand, if ABC123 is freely placed in every frame, the permutation is 6!.

Hence, the ratio is 6*6/6! = 1/20.


```{r}
sims <- 100000
children <- c("girl","girl","girl","boy","boy","boy")
event <- 0


for (i in 1:sims) {
  orders <- sample(x=children, size=6, replace=FALSE)
  if (orders[1]=="girl" & orders[2]=="girl" & orders[3]=="girl"){
    event <- event+1
  }
}

answer <- event/sims
answer
```


Problem 38 part (a)
There are doors named 1~7.
Assume that you will choose the door 1 at first and the car is actually in the door2(this condition will be explained as C2).

When you don't change your choice, the probability of winning is 1/7.
(This is because there are 7 doors)

When you switch to the door2, the possibility of winning a car is 
 P (winning |C2)* 1/7 = 1/3 *1/7= 1/21.

(The last choice has a probability of 1/3, since only one of the three remaining choices is a winner. Also,The probability of a car being at door 2 is 1/7, since there are seven doors.)

The same calculation would be done for each of the doors 2 through 7 per door,
1/21+1/21+1/21+1/21+1/21+1/21
=1/21*6 =2/7

Therefore, you should swtch the door. The probability of success if you switch the door is 2/7.

```{r}
sims <- 100000
doors <- c("goat", "goat", "goat", "goat", "car", "goat", "goat")
result.switch <- result.noswitch <- rep(NA, sims)

  for (i in 1:sims) {
  ## randomly choose the initial door
  initialdoor <- sample(1:7, size = 1)
  result.noswitch[i] <- doors[initialdoor]
  remain <- doors[-initialdoor] # remaining six doors after initial door is chosen
  ## Monty chooses three doors with a goat
  if (doors[initialdoor] == "car"){ # initial door holds the car
    monty <- sample(1:6, size=3)
  } else{ # 5 goats and one car left
    car_placement <- which(grepl("car", remain))
    tmp <- c(1,2,3,4,5,6)
    monty <- sample(tmp[tmp!=car_placement], 3)
  }
    remain_stp2 <- remain[-monty] 
    result.switch[i] <- sample(remain_stp2, 1)
  }
  
mean(result.noswitch == "car")
mean(result.switch == "car")
```

