---
title: "B2 homework2 predicting course grades"
author: "satsuki gyoten"
date: "2023-10-04"
output: html_document
---
```{r}
grades<-read.csv("grades.csv")
head(grades)
```
Predicting Course Grades Using Midterm Scores

```{r}
cor(grades$midterm,grades$final)
```

1
a.students
b. midterm will be our X variable
c. final  will be our Y variable
d. 0.7160323
```{r}
lm(grades$final~grades$midterm)

```


```{r}
# 2-a

plot(x=grades$midterm ,y= grades$final)
fit<-lm(grades$final~grades$midterm)


# 2-c

abline(fit)
```
2
b. final=  -6.0059+ 0.9704*midterm

```{r}
# a 
-6.0059+ 0.9704*80

# b 
-6.0059+ 0.9704*90

# c 
0.9704*10

```
3
a The best guess of the final exam score is 71.6261 points.
bThe best guess of the final exam score is 81.3301 points.
c The score will increase by  9.704 points.

```{r}
cor(x= grades$midterm, y=grades$final )^2
```

4
0.5127023

R^2 takes values between 0 and 1. When the number is closer to 0, the worse the accuracy is, and if it is the closer to 1, the better the accuracy of the regression equation. In this case, the value is roughly 0.5, so the accuracy can be evaluated as slightly better.