---
title: "B4"
author: "satsuki gyoten"
date: "2023-11-07"
output: html_document
---
1.
```{r}
set.seed(36850) # set random seed so that you get the same output everytime even though it's "random"

sample_space_coin <- c("H", "T")
event_probs_coin <- c(0.5, 0.5)


coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coin,
    prob = event_probs_coin,
    replace = TRUE
  )
}

coin_flip()

```
From the code above, we can simulate a coin flip. 
When coin_flip() was called 10 times, the result was A. This shows that the chances of getting each side of the coin are actually about 0.5 each.

2.
```{r}
set.seed(36850)
flip1 <- coin_flip()
flip2 <- coin_flip()
flip3 <- coin_flip()
flip4 <- coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 # H
flip2 # T
flip3 # T
flip4 # H

# Function that acts like a random variable.
# returns 1 if flip == "H" and 0 otherwise.

X_coin <- function(flip){
  ifelse(flip == "H",1,0)
}


# The code below should return a 1 for flip1 and flip4 and 0 for flip2 and flip3
X_coin(flip1)
X_coin(flip2)
X_coin(flip3)
X_coin(flip4)
```
3.
Treating `X_coin()` like a random variable describe it:
  a. What is the probability of 1? ->0.5
  b. What is the probability of 0? ->0.5
  c. What is the expectation of `X_coin()`?->0.5
  d. What is the variance of `X_coin()`?-> 0.25


4. Define a new function `biased_coin_flip()` that acts like `coin_flip()` except it returns "H" 70 percent of the time.
```{r}
set.seed(36850) # set random seed so that you get the same output everytime even though it's "random"

sample_space_coinb <- c("H", "T")
event_probs_coinb <- c(0.7, 0.3)

biased_coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coinb,
    prob = event_probs_coinb,
    replace = TRUE
  )
}

biased_coin_flip()

```

5. Define a new random variable `X_biased_coin()` that returns a 1 if flip is "H" and returns 0 if flip is "T"
```{r}
set.seed(36850)
flip1 <- biased_coin_flip()
flip2 <- biased_coin_flip()
flip3 <- biased_coin_flip()
flip4 <- biased_coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 # H
flip2 # T
flip3 # T
flip4 # H

# Function that acts like a random variable.
# returns 1 if flip == "H" and 0 otherwise.

X_biased_coin <- function(flip){
  ifelse(flip == "H",1,0)
}


# The code below should return a 1 for flip1 and flip4 and 0 for flip2 and flip3
X_biased_coin(flip1)
X_biased_coin(flip2)
X_biased_coin(flip3)
X_biased_coin(flip4)
```
5. Using math, calculate:
  a. The expectation of `X_coin()`
      0.5*1+0.5*0=0.5
  b. The expectation of `X_biased_coin()`
    0.7*1+0.3*0=0.7
  c. The expectation of `X_coin()` + `X_biased_coin()`
   X_coin()` + `X_biased_coin()`=
   0.5+0.7=1.2
   
6. Use simulation to estimate:
  a. The expectation of `X_coin()`
  
```{r}
sims <- 100000
coin <- c("H","T")
event <-0
event2 <-0

for (i in 1:sims) {
  flip <- sample(x=coin, size=1, replace=TRUE)
   if (flip =="H" ){
    event <- event+1
   }
   else{
    event2 <- event2+1
   }
}

 event/sims
 event2/sims
```
from the code above, we can say that the probability of getting an "H" and tail is both around 0.5.
Therefore, the expectation of X_coin() is
 0.5*1+0.5*0=0.5
 
 
  
  b. The expectation of `X_biased_coin()`
```{r}
sims <- 100000
coin <- c("H","T")
prob <- c(0.7, 0.3)  
event <-0
event2 <-0

for (i in 1:sims) {
  flip <- sample(x=coin, size=1, replace=TRUE, prob=prob)
   if (flip=="H" ){
    event <- event+1
   }
   else{
    event2 <- event2+1
   }
}

event/sims
event2/sims
```
from the code above, we can say that the probability of getting an "H" and tail is both around 0.5.
Therefore, the expectation of X_coin() is
0.7*1+0.3*0=0.7
 
  c. The expectation of `X_coin()` + `X_biased_coin()`
```{r}
sims <- 100000
coin <- c(1,0)
prob <- c(0.5, 0.5)  

flips <- rep(NA, sims)

for (i in 1:sims) {
  flips[i] <- sample(x=coin, size=1, replace=TRUE, prob=prob)
}

mean(flips)
```

```{r}
sims <- 100000
coin <- c(1,0)
prob <- c(0.7, 0.3)  

flips <- rep(NA, sims)

for (i in 1:sims) {
  flips[i] <- sample(x=coin, size=1, replace=TRUE, prob=prob)
}

mean(flips)



```
from the code above, the expectation of `X_coin()` + `X_biased_coin()`
is 1.2.

