---
title: "B4"
author: "satsuki gyoten"
date: "2023-11-07"
output: html_document
---
1.
```{r}
set.seed(36850) # set random seed so that you get the same output everytime even though it's "random"

sample_space_coin <- c("H", "T")
event_probs_coin <- c(0.5, 0.5)


coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coin,
    prob = event_probs_coin,
    replace = TRUE
  )
}

coin_flip()

```
From the code above, we can simulate a coin flip. 
When coin_flip() was called 10 times, the result was A. This shows that the chances of getting each side of the coin are actually about 0.5 each.

2.
```{r}
set.seed(36850)
flip1 <- coin_flip()
flip2 <- coin_flip()
flip3 <- coin_flip()
flip4 <- coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 # H
flip2 # T
flip3 # T
flip4 # H

# Function that acts like a random variable.
# returns 1 if flip == "H" and 0 otherwise.

X_coin <- function(flip){
  ifelse(flip == "H",1,0)
}


# The code below should return a 1 for flip1 and flip4 and 0 for flip2 and flip3
X_coin(flip1)
X_coin(flip2)
X_coin(flip3)
X_coin(flip4)
```
3.
Treating `X_coin()` like a random variable describe it:
  a. What is the probability of 1? ->0.5
  b. What is the probability of 0? ->0.5
  c. What is the expectation of `X_coin()`?->0.5
  d. What is the variance of `X_coin()`?-> 0.25


4. Define a new function `biased_coin_flip()` that acts like `coin_flip()` except it returns "H" 70 percent of the time.
```{r}
set.seed(36850) # set random seed so that you get the same output everytime even though it's "random"

sample_space_coinb <- c("H", "T")
event_probs_coinb <- c(0.7, 0.3)

biased_coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coinb,
    prob = event_probs_coinb,
    replace = TRUE
  )
}

biased_coin_flip()

```

5. Define a new random variable `X_biased_coin()` that returns a 1 if flip is "H" and returns 0 if flip is "T"
```{r}
set.seed(36850)
flip1 <- biased_coin_flip()
flip2 <- biased_coin_flip()
flip3 <- biased_coin_flip()
flip4 <- biased_coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 # H
flip2 # T
flip3 # T
flip4 # H

# Function that acts like a random variable.
# returns 1 if flip == "H" and 0 otherwise.

X_biased_coin <- function(flip){
  ifelse( biased_coin_flip() == "H",1,0)
}


# The code below should return a 1 for flip1 and flip4 and 0 for flip2 and flip3
X_biased_coin(flip1)
X_biased_coin(flip2)
X_biased_coin(flip3)
X_biased_coin(flip4)
```
5. Using math, calculate:
  a. The expectation of `X_coin()`
      0.5*1+0.5*0=0.5
  b. The expectation of `X_biased_coin()`
    0.7*1+0.3*0=0.7
  c. The expectation of `X_coin()` + `X_biased_coin()`
  E( X_coin()` + `X_biased_coin())`= E X_coin()`+E X_biased_coin()
   0.5+0.7=1.2
   
6. Use simulation to estimate:
  a. The expectation of `X_coin()`
  
```{r}
sims <- 100000
coin <- c("H","T")
event <-0
event2 <-0

for (i in 1:sims) {
  flip <- sample(x=coin, size=1, replace=TRUE)
   if (flip =="H" ){
    event <- event+1
   }
   else{
    event2 <- event2+1
   }
}

 event/sims
 event2/sims
```
from the code above, we can say that the probability of getting an "H" and tail is both around 0.5.
Therefore, the expectation of X_coin() is
 0.5*1+0.5*0=0.5
or, it can be caluvulated like below
```{r}
sims <- 100000
coin <- c(1,0)
prob <- c(0.5, 0.5)  

flips <- rep(NA, sims)

for (i in 1:sims) {
  flips[i] <- sample(x=coin, size=1, replace=TRUE, prob=prob)
}

mean(flips)
```
 
  
  b. The expectation of `X_biased_coin()`
```{r}
sims <- 100000
coin <- c("H","T")
prob <- c(0.7, 0.3)  
event <-0
event2 <-0

for (i in 1:sims) {
  flip <- sample(x=coin, size=1, replace=TRUE, prob=prob)
   if (flip=="H" ){
    event <- event+1
   }
   else{
    event2 <- event2+1
   }
}

event/sims
event2/sims
```
from the code above, we can say that the probability of getting an "H" and tail is both around 0.5.
Therefore, the expectation of X_coin() is
0.7*1+0.3*0=0.7

or, it can be calculated like below,
```{r}
sims <- 100000
coin <- c(1,0)
prob <- c(0.7, 0.3)  

flips <- rep(NA, sims)

for (i in 1:sims) {
  flips[i] <- sample(x=coin, size=1, replace=TRUE, prob=prob)
}

mean(flips)



```
 
 c. The expectation of `X_coin()` + `X_biased_coin()`
```{r}
set.seed(36850)

nsims <- 100000

# vectors where you can store the results of simulation for a, b, and c
X_coin_sims <- vector(mode = 'numeric', length = nsims)
X_biased_coin_sims <- vector(mode = 'numeric', length = nsims)
unbiased_plus_biased_coin_sims <- vector(mode = 'numeric', length = nsims)


for(i in 1:nsims){
  sim_flip_i <- coin_flip()
  X_coin_sims[i] <- X_coin(sim_flip_i)
  
  sim__biasedflip_i <- biased_coin_flip
  X_biased_coin_sims[i] <- X_biased_coin(sim__biasedflip_i)
  
  unbiased_plus_biased_coin_sims[i] <- X_coin_sims[i]+X_biased_coin_sims[i] 
  
}

# use head to see the first part of the result of the simulations
head(unbiased_plus_biased_coin_sims)

# calculate the expectation of the simulations using mean()
mean( unbiased_plus_biased_coin_sims)



```


from the code above, the expectation of `X_coin()` + `X_biased_coin()`
is 1.2.


7. Imagine an experiment similar to the one we discussed. Students can use a drug, Getana. We are interested in studying the effect of Getana on student's GPA. In the code below, I've defined:
  a. A student index 1-6, it just assignes each student a number.
  b. A potential outcome for each student under treatement, Y1, and control, Y0. Note that the potential outcomes are the same, indicating that there is 0 effect
```{r}
student_index <- 1:6
Y1 <- c(4, 4, 3, 2, 1,1)
Y0 <- Y1
```
Now, simulate what happens if we randomly sample 1 student to be in the Treatment group (so we see their GPA under Y1), and we sample a different student to be in Control (so we see their GPA under Y0). What will the average difference in GPA's be between the Treatment subject and Control subject? Compare the results to what you get if you simply subtract the mean of Y0 from the mean of Y1.

```{r}
set.seed(36850)

nsims <- 100000

gpa_treat_minus_control_sims <- vector(mode = "numeric",
                                       length = nsims)

for(i in 1:nsims){
  treated_subj_index <- sample(student_index, 
                               size = 1)
  control_subj_index <- sample(student_index[-treated_subj_index], 
                               size = 1)
  observed_treatement_GPA <- Y1[treated_subj_index]
  observed_control_GPA <- Y0[control_subj_index]
    
  gpa_treat_minus_control_sims[i] <- observed_treatement_GPA - observed_control_GPA # What is the observed difference in gpas between treatment and control subjects?
}

# Calculate the average of gpa_treat_minus_control_sims
mean(gpa_treat_minus_control_sims)
mean(Y1 - Y0)
```
Create a histogram of `gpa_treat_minus_control_sims` using ggplot. Make it look as good as you can, with proper axis labels.

```{r}
library(tidyverse)
library(ggplot2)
```
```{r}

df <- data.frame(gpa_treat_minus_control_sims)

ggplot(data = df, mapping = aes(gpa_treat_minus_control_sims)) +
  geom_histogram(binwidth = 1, fill = "red", color = "white") +
  labs(x = "gap", y = "counts", title = "gpa_treat_minus_control")
          
```

